---
title: "toolsheff"
format: gfm
---

Collection of general use functions. The to-do list is noted under [github.com/scc-pi/toolsheff/issues](https://github.com/scc-pi/toolsheff/issues).

## Use

To use the functions, add the following at the top of your R script (or in your `setup` R Markdown or Quarto chunk):

```{r}
#| eval: FALSE
source("https://raw.githubusercontent.com/scc-pi/toolsheff/main/R/_scc-tools.R")
```

## Development  

If you've branched from `main` and are developing the functions, and want to use (or test) them, you could source from your local repo, for example:   

```{r}
#| eval: FALSE
# source("https://raw.githubusercontent.com/scc-pi/toolsheff/main/R/_scc-tools.R")
source("C:/repo/toolsheff/R/_scc-tools.R")
```

## Project specific  

You may have functions that are useful across different scripts but only within the context of a single project. In this scenario, you could add a similar script with functions (for example `_scc-tools-housing.R`), but within your project specific repo (for example [github.com/scc-pi/housing](https://github.com/scc-pi/housing)) rather than this repo ([github.com/scc-pi/toolsheff](https://github.com/scc-pi/toolsheff)). In which case you'd need to source a second file, for example: 

```{r}
#| eval: FALSE
# source("https://raw.githubusercontent.com/scc-pi/toolsheff/main/R/_scc-tools.R")
source("C:/repo/toolsheff/R/_scc-tools.R")
source(here::here("R", "_scc-tools-housing.R"))
```

## Database connections

Even with hidden authorisation credentials, we don't want to store database addresses and port numbers in a public repo. So, this is something that will have to wait until we have secure private repos available via Azure DevOps.

## Plans  

Data analysis at Sheffield Council is set to switch its default Git repository hosting from GitHub to Azure DevOps. When it does, we'll look at creating R packages for internal use via Continuous Integration. Until then this is a workaround.    

## `{box}` R package  

We've briefly tried the `{box}` R package to support modular code: [klmr.me/box](https://klmr.me/box/). We may review our use of it after we've established the convenience (or otherwise) of internal packages via Continuous Integration in Azure DevOps.    
